Lensing

### 2015-01-19 Papers/ms.tex
Tinkering

\section{Introduction}
Strong gravitational lensing is a powerful astrophysical tool for studying
the distribution of matter, including dark matter, in galaxies
\citep{treu}.

\subsection{The hunt for dark substructures}
In recent years, several galaxy-galaxy lens systems have been discovered which
are thought to contain at least one dark substructure
\citep{vegetti1, vegetti2, vegetti3}.

>>>>

\section{Introduction}
Galaxy-galaxy lensing is a powerful astrophysical tool for studying
the distribution of matter, including dark matter, in galaxies
\citep{treu}.

In recent years, several lens systems have been discovered which
are thought to contain at least one dark substructure
\citep{vegetti1, vegetti2, vegetti3}.

In this paper we address the topic of inferring the matter distribution in the
lens galaxy from the lensed, blurred image.
